---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ltdecomp

<!-- badges: start -->
<!-- badges: end -->

The goal of ltdecomp is to build simple life-tables from mortality data and 
then perform life-table decompositions to isolate the contribution of specific 
causes of death to life-expectancy. The package is designed for private use on 
historical mortality data, but should work for any collection of information on
populations and associated numbers of deaths. 

## Installation

You can install the development version of ltdecomp from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gabrielfgm/ltdecomp")
```

## Example

This is a basic example of constructing a lifetable:

```{r example}
library(ltdecomp)
## basic example code

# Age groups
Age <-  c("0", "1-4", "5-9", "10-14", "15-19", "20-24", "25-29", "30-34", 
          "35-39", "40-44", "45-49", "50-54", "55-59", "60-64", "65-69",
          "70-74", "75-79", "80-84", "85-89", "90-94", "95+") 

# Death counts
Dx <- c(110934, 17693, 9168, 7378, 12192, 13356, 14223, 19210, 29136, 42961, 64310, 
        90630, 116759, 153504, 196682, 223796, 220065, 185305, 120414, 50299, 13887)

# mid year population
Px <- c(4126560, 16195304, 18659141, 16815965, 13287434, 10803165, 10870165,
        11951709, 12508316, 11567216, 10528878, 9696502, 8595947, 7111897, 6186763,
        4661136, 2977347, 1518206, 648581, 170653, 44551)

lifetable(age = Age, Dx = Dx, Px = Px)

```


